### 2021-07-03 docs/manuscript/manuscript.tex
Add info about diffusion and degradation parameters

However, as our model was less stringent and allowed the morphogen input to
interact with any gene, we found a larger number of possible topologies with the
same striped phenotype. For example, in a single input model the I4-FFL could
not produce a stripe of gene expression~\cite{munteanu_2014}, whereas in our
experimental setup 20.17\% of the topologies presented this motif as a
subgraph~(\nameref{S1_Table}).

@@

>>>>

However, as our model was less stringent and allowed the morphogen input to
interact with any gene, we found a larger number of possible topologies with the
same striped phenotype and a diverse combination of diffusion and degradation
parameters (\nameref{S6_Fig}).
For example, in a single input model the I4-FFL could
not produce a stripe of gene expression~\cite{munteanu_2014}, whereas in our
experimental setup 20.17\% of the topologies presented this motif as a
subgraph~(\nameref{S1_Table}).

@@

\paragraph*{S6 Fig.}
\label{S6_Fig}
{\bf Diffusion and degradation parameters.}
(A) Ternary plot showing the combination of diffusion parameters for genes A,
B and C. (B) Ternary plot showing the combination of degradation parameters
for genes A, B and C.
